Precision calculations of the cosmic shear power spectrum projection

### 2017-04-20 limber2.tex
First draft of referee reply and modifications.

\newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}
\newcommand{\Label}[1]{\quad (\mbox{#1})}
\newcommand{\LabelTxt}[1]{(\mbox{#1})}

@@

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations are negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by Kitching et al. (2016, version 1)

@@

In the era of the upcoming large-scale surveys that will provide measurements
of cosmic shear with unprecedented precision, one needs to revisit the
theoretical predictions of the observables to ensure that the accuracy of the
models meet the accuracy of the observations. In this paper, we examine the
widely used Limber approximation for the projected weak-lensing power spectrum.
We consider spherical coordinates and the flat-sky approximation, and compute
the full projection. The first-order extended Limber approximation provides
sub-percent accuracy for $\ell > 10$ and is sufficient for present surveys. The
associated errors are sub-dominant even for future large surveys.

@@

This paper is organised as follows.  In section~\ref{sec:wl} we provide a
pedagogical introduction to weak gravitational lensing theory, projections and
power spectra for the flat-sky and spherical cases, following the seminal work
from \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
section~\ref{sec:L2} we derive weak-lensing observables using a second-order
Limber approximation first introduced by \citet{2008PhRvD..78l3506L}. We
compare the shear power spectrum and the commonly-used two-point shear
correlation function for the full solution to a range of different
approximations in section~\ref{sec:results}, providing cosmological constraints
for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo}. This paper
draws from several sources of literature which have previously discussed the
full projection, or reviewed the accuracy of the Limber approximation for weak
lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B,
2012MNRAS.422.2854G, 2016arXiv161104954K}. We present a discussion and
comparison of our results to these papers in Appendix~\ref{app:B}.

@@

This type of cross-power spectrum between different cosmological epochs
$\chi$ and $\chi^\prime$ was introduced in \cite{2005PhRvD..72b3516C}. In
Sects.~\ref{sec:geom_mean} and \ref{sec:factor_D} this unequal-time
cross-spectrum \citep{2016arXiv161200770K} will be further evaluated and
simplified in the context of the Limber approximation. The oscillating Bessel
functions in equation~(\ref{eq:C_ell_phi_Pm}) ensure that only relatively close epochs
contribute to the lensing potential correlation. This make sense since observed
light rays from two galaxies at different positions on the sky that necessarily
converge at the observer today, pick up the density fluctuations at similar
times while propagating through the large-scale structure. A similar argument
has been made in \cite{BS01}: since the matter power spectrum scales with $k$
for $k \rightarrow 0$, there is decreasing power towards larger and larger
scales. In particular, the correlation of cosmic fields decreases strongly
above a coherence scale $|\chi - \chi^\prime| \gsim L_{\rm coh}$ which is significantly
smaller than the horizon scale $\chi_{\rm h}$.

@@

The tomographic shear power spectrum, in analogy to equation~(\ref{eq:C_ell_phi_Pm}), is defined by
%
\begin{equation}
  \left\langle _2\gamma^{}_{\ell m, i} \; {}_2\gamma^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\gamma_{ij}(\ell).
  \label{eq:C_ell_gamma}
\end{equation}
%
%For a zero-curvature Universe, this is given by
This is given by
%
\begin{align}
  C^\gamma_{ij}(\ell) = \frac 1 4 \ellbar^2(\ell, 2) \, C^\psi_{ij}(\ell)
                 = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime), \Label{FullSph}
  \label{eq:C_ell_full}
\end{align}
%
where we use the label `FullSph', see Table \ref{tab:cases} for a list of cases discussed in this work.
The spherical spin pre-factor for the full projection shear power
spectrum is $\ellbar^2(\ell, 2)$, which will be modified under
flat-sky and Limber approximations below.

@@

The majority of cosmic shear analyses have used the predicted lensing power
spectrum approximated on a flat sky, neglecting the sky curvature. This is a
valid approach for past and current survey areas with an extent less than 10
degrees. To account for the sky curvature of the observed data, the shear
correlation functions from observed galaxy ellipticities is now routinely
computed using spherical coordinates, since projecting to a Cartesian plane has
been shown to cause significant biases of the two-point funtion on large scales
\citep{FSHK08}, and lead to spurious B-modes \citep{asgari/etal:2017}. Here
we examine the effect of sky curvature on the theoretical models of the power
spectrum, and the effect on cosmological parameter inference (see
Sect.~\ref{sec:cfhtlens}).

@@

The flat-sky power spectrum, i.e. the flat-sky analogue of equation~(\ref{eq:C_ell_psi}), is defined by
%
\begin{equation}
  \left\langle \hat \psi_i^{}(\vec \ell) \hat \psi_j^\ast(\vec \ell^\prime) \right\rangle
    = (2\pi)^2 \delta_{\rm D}(\vec \ell - \vec \ell^\prime) P^\psi_{ij}(\ell).
  \label{eq:P_ell_psi}
\end{equation}
%
\cite{2000PhRvD..62d3007H} has shown that for small angles the harmonics
expansion (equation~\ref{eq:psi_harm_exp}) can be approximated by the Fourier
representation in equation~(\ref{eq:psi_fourier}). They also demonstrated that the power
spectra are approximately equal, $P^\psi \approx C^\psi$.

For a spin-2 field, \cite{2000PhRvD..62d3007H} approximates the edth operator
by Cartesian derivatives, and approximates equation~(\ref{eq:sYlm_def}) as
%
\begin{equation}
  \ell^2 \, _{\pm2}\!{\rm Y}_{\ell m}(\theta, \varphi) \approx  {\rm e}^{{\mp}2 {\rm i} \phi_\ell}
    (\partial_1 \pm {\rm i} \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
  \label{eq:sYlm_def_flat}
\end{equation}
%
The spin pre-factor $\ellbar(\ell, 2) = \sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$
is replaced by $\ell^2$ in flat co-ordinates, an approximation that holds for
large $\ell$, since sky curvature can be neglected for small angular
scales. We find for the flat-sky shear power spectrum
%
\begin{align}
  P^\gamma_{ij}(\ell) 
                 = & \frac 2 \pi \, \ell^4 \, \pref^2
                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:P_ell_gamma_full_der}
\end{align}
%
with flat-sky pre-factor $\ell^4$. See App.~\ref{sec:schmidt08} and
\ref{sec:giannantonio12} for discussions of alternative expressions for the
flat-sky power spectrum.

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. We apply their general derivation to the case of weak lensing,
and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power
spectrum using two approaches presented in Sects.~\ref{sec:geom_mean} and
\ref{sec:factor_D}.

First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
  \label{eq:jJ}
\end{equation}
%
in equation~(\ref{eq:C_ell_full}), where ${\rm J}_\nu$ is the Bessel function of the first kind
and order $\nu$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_\nu(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_\nu(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of an arbitrary differentialble function
$f$ around $x = k \chi = \nu = \ell + 1/2$, where the Bessel function has its
approximate maximum.

@@

To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor of
the power spectrum,
%
\begin{equation}
 P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi).
  \label{eq:P_k_chi_sep_s}
\end{equation}
%
The function $\tilde P_{\rm m}$ is in general not time-independent, except
in the case of a linear matter power spectrum in the absence of massive
neutrinos, and in General Relativity. However, the second-order Limber terms
are expected to be important only for small $\ell$, since for large $\ell$ the first-order
Limber equation (\ref{eq:C_ell_limber1}) is dominant. Eq.~(\ref{eq:P_k_chi_sep_s})
becomes a good approximation for small $\ell$, since that means either small
$k$ where the evolution is linear, or small $\chi$, where the lensing
efficiency is small. The accuracy of a very nearby tomographic bin with low
mean redshift should be further examined, but this is not the case for
CFHTLenS.

@@

The extended flat-sky Limber approximation is readily derived from the
spherical case equations~(\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, p(\ell) \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \frac{\pref^2}{2}
    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
    %\nonumber \\
    %& \times
    \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Further approximations can be made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the
    \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
  i.e.~for all pre-2014 CFHTLenS results and DLS
  \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
  we do not discuss the second-order Limber approximation with $p(\ell)=1$.
  %
  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the
  \emph{extended} Limber approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with
  $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
  %
  \item $p(\ell) = 1$, but keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
    a \emph{hybrid} between
    standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017,abbott/etal:2016}. As is shown
    below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
    the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.
\end{enumerate}

@@

\renewcommand{\baselinestretch}{1.5}
\begin{table}
\begin{centering}
  %
  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the label
    used in the text and figures.
    The third column shows the power-spectrum pre-factor $p(\ell)$. } 
    %
    \begin{tabular}{|l|l|c|c|c|p{0.21\textwidth}}
  \hline
  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & Comment \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Pre-2014 CFHTLenS and DLS \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & ExtL2Fl &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ 
    & $\ell+\frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  %
  $2^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
    & $1$ 
    & $\ell+ \frac 1 2$ & Best flat-sky approximation \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & Best approximation \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      - & - & Correct projection \\ \hline
  %
  \end{tabular}

@@

The majority of cosmic shear analyses to date have adopted real-space
correlation statistics, since these can be measured directly from an observed
galaxy shape catalogue. The baseline quantity is the two-point correlation
function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given by
%
\begin{align}
  \xi_+(\theta) 
  % &
  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
   \theta)
  P^\gamma(\ell);
  \quad
  %\nonumber \\
   %
   \xi_-(\theta)
  %&
  = \frac 1 {2\pi} \int
   {\rm d} \ell \, \ell \, {\rm J}_4(\ell \theta)
  P^\gamma(\ell).
  %
   \label{eqn:xiGG}
\end{align}
%
The flat-sky shear power spectrum $P^\gamma$ can be related to the underlying
matter power spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a
first-order extended Limber approximation, or equation~(\ref{eq:P_ell_limber2})
when adopting a second-order extended Limber approximation.

>>>>

\definecolor{darkred}{rgb}{0.8,0.1,0.1}
\newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}
\newcommand{\EDIT}[1]{{\bf\textcolor{red}{#1}}}
\newcommand{\forref}[1]{{\bf\textcolor{darkred}{#1}}}
\newcommand{\Label}[1]{\quad (\mbox{#1})}
\newcommand{\LabelTxt}[1]{(\mbox{#1})}

@@

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations \forref{is} negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by Kitching et al. (2016, version 1)

@@

In the era of the upcoming large-scale surveys that will provide measurements
of cosmic shear with unprecedented precision, one needs to revisit the
theoretical predictions of the observables to ensure that the accuracy of the
models meet the accuracy of the observations. In this paper, we examine the
widely used Limber approximation for the projected weak-lensing power spectrum.
We consider spherical coordinates and the flat-sky approximation, and compute
the full projection \forref{of the lensing power spectrum}. The first-order
extended Limber approximation provides sub-percent accuracy for $\ell > 10$ and
is sufficient for present surveys. The associated errors are sub-dominant even
for future large surveys.

@@

This paper is organised as follows.  In section~\ref{sec:wl} we provide a
pedagogical introduction to weak gravitational lensing theory, projections and
power spectra for the flat-sky and spherical cases, following the seminal work
\forref{by} \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
section~\ref{sec:L2} we derive weak-lensing observables using a second-order
Limber approximation first introduced by \citet{2008PhRvD..78l3506L}. We
compare the shear power spectrum and the commonly-used two-point shear
correlation function for the full solution to a range of different
approximations in section~\ref{sec:results}, providing cosmological constraints
for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo}. This paper
draws from several sources of literature which have previously discussed the
full projection, or reviewed the accuracy of the Limber approximation for weak
lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B,
2012MNRAS.422.2854G, 2016arXiv161104954K}\forref{, see also
\cite{2017arXiv170401054L} for a more recent work.} We present a discussion and
comparison of our results to these papers in Appendix~\ref{app:B}.

@@

This type of cross-power spectrum between different cosmological epochs
$\chi$ and $\chi^\prime$ was introduced in \cite{2005PhRvD..72b3516C}. In
Sects.~\ref{sec:geom_mean} and~\ref{sec:factor_D} this unequal-time
cross-spectrum \citep{2016arXiv161200770K} will be further evaluated and
simplified in the context of the Limber approximation. The oscillating Bessel
functions in equation~(\ref{eq:C_ell_phi_Pm}) ensure that only relatively close epochs
contribute to the lensing potential correlation. This make sense since observed
light rays from two galaxies at different positions on the sky that necessarily
converge at the observer today, pick up the density fluctuations at similar
times while propagating through the large-scale structure. A similar argument
has been made in \cite{BS01}: since the matter power spectrum scales with $k$
for $k \rightarrow 0$, there is decreasing power towards larger and larger
scales. In particular, the correlation of cosmic fields decreases strongly
above a coherence scale $|\chi - \chi^\prime| \gsim L_{\rm coh}$ which is significantly
smaller than the horizon scale $\chi_{\rm h}$.

@@

The tomographic shear power spectrum, in analogy to equation~(\ref{eq:C_ell_phi_Pm}), is defined by
%
\begin{equation}
  \left\langle _2\gamma^{}_{\ell m, i} \; {}_2\gamma^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\gamma_{ij}(\ell).
  \label{eq:C_ell_gamma}
\end{equation}
%
%For a zero-curvature Universe, this is given by
This is given by
%
\begin{align}
  C^\gamma_{ij}(\ell) = \frac 1 4 \ellbar^2(\ell, 2) \, C^\psi_{ij}(\ell)
                 = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime), \Label{FullSph}
  \label{eq:C_ell_full}
\end{align}
%
where we use the label `FullSph', see Table~\ref{tab:cases} for a list of cases discussed in this work.
The spherical spin pre-factor for the full projection shear power
spectrum is $\ellbar^2(\ell, 2)$, which will be modified under
flat-sky and Limber approximations below.

@@

The majority of cosmic shear analyses have used the predicted lensing power
spectrum approximated on a flat sky, neglecting the sky curvature. This is a
valid approach for past and current survey areas with an extent less than 10
degrees. To account for the sky curvature of the observed data, the shear
correlation functions from observed galaxy ellipticities \forref{are} now routinely
computed using spherical coordinates, since projecting to a Cartesian plane has
been shown to cause significant biases of the two-point funtion on large scales
\citep{FSHK08}, and lead to spurious B-modes \citep{asgari/etal:2017}. Here
we examine the effect of sky curvature on the theoretical models of the power
spectrum, and the effect on cosmological parameter inference (see
Sect.~\ref{sec:cfhtlens}).

@@

The flat-sky power spectrum, i.e.\ the flat-sky analogue of equation~(\ref{eq:C_ell_psi}), is defined by
%
\begin{equation}
  \left\langle \hat \psi_i^{}(\vec \ell) \hat \psi_j^\ast(\vec \ell^\prime) \right\rangle
    = (2\pi)^2 \delta_{\rm D}(\vec \ell - \vec \ell^\prime) P^\psi_{ij}(\ell).
  \label{eq:P_ell_psi}
\end{equation}
%
\cite{2000PhRvD..62d3007H} has shown that for small angles the harmonics
expansion (equation~\ref{eq:psi_harm_exp}) can be approximated by the Fourier
representation in equation~(\ref{eq:psi_fourier}). They also demonstrated that the power
spectra are approximately equal, $P^\psi \approx C^\psi$.

For a spin-2 field, \cite{2000PhRvD..62d3007H} approximates the edth operator
by Cartesian derivatives, and approximates equation~(\ref{eq:sYlm_def}) as
%
\begin{equation}
  \ell^2 \, _{\pm2}\!{\rm Y}_{\ell m}(\theta, \varphi) \approx  {\rm e}^{{\mp}2 {\rm i} \phi_\ell}
    (\partial_1 \pm {\rm i} \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
  \label{eq:sYlm_def_flat}
\end{equation}
%
The spin pre-factor $\ellbar(\ell, 2) = \sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$
is replaced by $\ell^2$ in flat co-ordinates, an approximation that holds for
large $\ell$, since sky curvature can be neglected for small angular
scales. We find for the flat-sky shear power spectrum
%
\begin{align}
  P^\gamma_{ij}(\ell) 
                 = & \frac 2 \pi \, \ell^4 \, \pref^2
                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:P_ell_gamma_full_der}
\end{align}
%
with flat-sky pre-factor $\ell^4$. See App.~\ref{sec:schmidt08} and~\ref{sec:giannantonio12} for discussions of alternative expressions for the
flat-sky power spectrum.

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. We apply their general derivation to the case of weak lensing,
and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power
spectrum using two approaches presented in Sects.~\ref{sec:geom_mean} and~\ref{sec:factor_D}.

First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
  \label{eq:jJ}
\end{equation}
%
in equation~(\ref{eq:C_ell_full}), where ${\rm J}_\nu$ is the Bessel function of the first kind
and order $\nu$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_\nu(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_\nu(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of an arbitrary \forref{differentiable} function
$f$ around $x = k \chi = \nu = \ell + 1/2$, where the Bessel function has its
approximate maximum.

@@

To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor of
the power spectrum,
%
\begin{equation}
 P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi) \forref{\approx D^2_+(\chi) \tilde P_{\rm m}(k)}.
  \label{eq:P_k_chi_sep_s}
\end{equation}
%
The function $\tilde P_{\rm m}$ is in general not time-independent, except
in the case of a linear matter power spectrum in the absence of massive
neutrinos, and in General Relativity. However, the second-order Limber terms
are expected to be important only for small $\ell$, since for large $\ell$ the first-order
Limber equation (\ref{eq:C_ell_limber1}) is dominant. Eq.~(\ref{eq:P_k_chi_sep_s})
becomes a good approximation for small $\ell$, since that means either small
$k$ where the evolution is linear, or small $\chi$, where the lensing
efficiency is small. The accuracy of a very nearby tomographic bin with low
mean redshift should be further examined, but this is not the case for
CFHTLenS.

@@

The extended flat-sky Limber approximation is readily derived from the
spherical case equations~(\ref{eq:C_ell_limber1},~\ref{eq:C_ell_limber2_dr_s}), by
replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, p(\ell) \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \frac{\pref^2}{2}
    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
    %\nonumber \\
    %& \times
    \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Further approximations can be made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the
    \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
  i.e.~for all pre-2014 CFHTLenS results and DLS
  \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
  we do not discuss the second-order Limber approximation with $p(\ell)=1$.
  %
  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the
  \emph{extended} Limber approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with
  $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
  %
  \item $p(\ell) = 1$, but keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
    a \emph{hybrid} between
    standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017,abbott/etal:2016}. As is shown
    below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
    the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.
\end{enumerate}

@@

\renewcommand{\baselinestretch}{1.5}
\begin{table}
\begin{centering}
  %
  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. `ID' is the label
    used in the text and figures.
    The third column shows the power-spectrum pre-factor $p(\ell)$. } 
    %
    \begin{tabular}{|p{0.22\textwidth}|l|c|c|c|c|c|p{0.21\textwidth}}
  \hline
  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & \forref{$\ell_{0.1}$} & \forref{$\ell_{0.01}$} & Comment \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat & L1Fl & (\ref{eq:P_ell_limber1})+(i)
    & $1$ & $\ell$ & $4$ & $60$ & Pre-2014 CFHTLenS and DLS \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat & ExtL1Fl & (\ref{eq:P_ell_limber1})+(ii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat & ExtL1FlHyb & (\ref{eq:P_ell_limber1})+(iii)
    & $1$ & $\ell + \frac 1 2$ & & & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & & & \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat & ExtL2Fl &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ 
    & $\ell+\frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  %
  $2^{\rm st}$-order extended Limber, hybrid, flat & ExtL2FlHyb &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
    & $1$ 
    & $\ell+ \frac 1 2$ & & & Best flat-sky approximation \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & & & Best approximation \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      - & - & - & - & Correct projection \\ \hline
  %
  \end{tabular}

@@

The majority of cosmic shear analyses to date have adopted real-space
correlation statistics, since these can be measured directly from an observed
galaxy shape catalogue. The baseline quantity is the two-point correlation
function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given \forref{in the flat-sky approximation} by
%
\begin{align}
  \xi_+(\theta) 
  % &
  = \forref{\left\langle \gamma \gamma^\ast \right\rangle(\theta) =} \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
   \theta)
  P^\gamma(\ell);
  \quad
  %\nonumber \\
   %
   \xi_-(\theta)
  %&
  = \forref{\left\langle \gamma \gamma \right\rangle(\theta) =} \frac 1 {2\pi} \int
   {\rm d} \ell \, \ell \, {\rm J}_4(\ell \theta)
  P^\gamma(\ell).
  %
   \label{eqn:xiGG}
\end{align}
%
The flat-sky shear power spectrum $P^\gamma$ can be related to the underlying
matter power spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a
first-order extended Limber approximation, or equation~(\ref{eq:P_ell_limber2})
when adopting a second-order extended Limber approximation.
